% this file was modified manually to include the spell description of "Invisibility".

% open a new spellcards environment
\begin{spellcard}{sor}{Invisibility, Greater}{4}
  % make the data from TSV accessible for to the LaTeX part:
  \newcommand{\name}{Invisibility, Greater}
  \newcommand{\school}{illusion}
  \newcommand{\subschool}{glamer}
  \newcommand{\descriptor}{NULL}
  \newcommand{\spelllevel}{4}
  \newcommand{\castingtime}{1 standard action}
  \newcommand{\components}{V, S}
  \newcommand{\costlycomponents}{0}
  \newcommand{\range}{personal or touch}
  \newcommand{\area}{NULL}
  \newcommand{\effect}{NULL}
  \newcommand{\targets}{NULL}% original: {you or creature touched}
  \newcommand{\duration}{1 round/level}
  \newcommand{\dismissible}{1}
  \newcommand{\shapeable}{0}
  \newcommand{\savingthrow}{Will negates (harmless)}
  \newcommand{\spellresistance}{yes (harmless)}
  \newcommand{\source}{PFRPG Core}
  \newcommand{\verbal}{1}
  \newcommand{\somatic}{1}
  \newcommand{\material}{0}
  \newcommand{\focus}{0}
  \newcommand{\divinefocus}{0}
  \newcommand{\deity}{NULL}
  \newcommand{\SLALevel}{4}
  \newcommand{\domain}{NULL}
  \newcommand{\acid}{0}
  \newcommand{\air}{0}
  \newcommand{\chaotic}{0}
  \newcommand{\cold}{0}
  \newcommand{\curse}{0}
  \newcommand{\darkness}{0}
  \newcommand{\death}{0}
  \newcommand{\disease}{0}
  \newcommand{\earth}{0}
  \newcommand{\electricity}{0}
  \newcommand{\emotion}{0}
  \newcommand{\evil}{0}
  \newcommand{\fear}{0}
  \newcommand{\fire}{0}
  \newcommand{\force}{0}
  \newcommand{\good}{0}
  \newcommand{\languagedependent}{0}
  \newcommand{\lawful}{0}
  \newcommand{\light}{0}
  \newcommand{\mindaffecting}{0}
  \newcommand{\pain}{0}
  \newcommand{\poison}{0}
  \newcommand{\shadow}{0}
  \newcommand{\sonic}{0}
  \newcommand{\water}{0}
  \newcommand{\linktext}{Invisibility, Greater}
  \newcommand{\id}{299}
  \newcommand{\materialcosts}{NULL}
  \newcommand{\bloodline}{NULL}
  \newcommand{\patron}{NULL}
  \newcommand{\mythictext}{NULL}
  \newcommand{\augmented}{NULL}
  \newcommand{\hauntstatistics}{NULL}
  \newcommand{\ruse}{0}
  \newcommand{\draconic}{0}
  \newcommand{\meditative}{0}
  \newcommand{\urlenglish}{https://www.d20pfsrd.com/magic/all-spells/i/invisibility/}
  \newcommand{\urlgerman}{http://prd.5footstep.de/Grundregelwerk/Zauber/Unsichtbarkeit\#h16029-1} % chktex 8
  % print the tabular information at the top of the card:
  \spellcardinfo[0.55]{}
  % draw a QR Code pointing at online resources for this spell on the front face:
  \spellcardqr{\urlenglish}
  % ATTENTION: URLs for foreign languages cannot be generated and must be provided by you!
  \spellcardqr{\urlgerman}
  % LaTeX-formatted description of the spell, generated from the HTML-formatted description_formatted column:
  This spell functions like \emph{invisibility,} except that it doesn't end if the subject attacks:

  The creature or object touched becomes invisible.
  If the recipient is a creature carrying gear, that vanishes, too.
  If you cast the spell on someone else, neither you nor your allies can see the subject,
  unless you can normally see invisible things or you employ magic to do so.

  Items dropped or put down by an invisible creature become visible;
  items picked up disappear if tucked into the clothing or pouches worn by the creature.
  Light, however, never becomes invisible, although a source of light can become so
  (thus, the effect is that of a light with no visible source).
  Any part of an item that the subject carries but that extends more than 10 feet from it becomes visible.

  Of course, the subject is not magically silenced, and certain other conditions
  can render the recipient detectable (such as swimming in water or stepping in a puddle).
  If a check is required, a stationary invisible creature has a +40 bonus on its Stealth checks.
  This bonus is reduced to +20 if the creature is moving.

  \emph{Invisibility} can be made permanent (on objects only) with a \emph{permanency} spell.

\end{spellcard}
